\documentclass[letterpaper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}
\usepackage{courier}
\usepackage[margin=0.75in]{geometry}
\usepackage{listings}
\usepackage{color}
\usepackage{graphicx}
\usepackage[width=5in]{caption}
\usepackage{hyphenat}
\usepackage{hyperref}

% Format a sectionless paragraph
\newcommand*\unparagraph{
	\par
	\nopagebreak
	\vskip3.25ex plus1ex minus.2ex
	\noindent
}

% define extra colors
\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{purple}{RGB}{159,0,197}

% define the code listing format
\lstset{
	language=C++,
	basicstyle=\footnotesize\ttfamily,
	backgroundcolor=\color{white},
	showspaces=false,
	showstringspaces=false,
	frame=none,
	tabsize=3,
	keywordstyle=\color{purple},
	commentstyle=\color{dkgreen},
	stringstyle=\color{blue},
	escapeinside={\%*}{*)}
}

% efine the title/header
\title{\Large CS 3468\\Syllabus} 
\author{Jared Wallace}
\date{}

\begin{document}

\maketitle

\vspace{30mm}

\section*{Meeting time and place}
Derrick Hall 236
Thursday at 8 am

\section*{Course Information}

A hands on opportunity to study the architecture of embedded systems and
micro-controllers, as well as their peripherals, languages, operating systems
and the special techniques required to use them.
\section*{Recommendations}
Each lab assignment will be posted one or more weeks in advance. It is absolutely
essential that you attend the lectures and study the material to be covered before
each lab. Do not count on a review or lecture before the lab from me. (Although I
will make every effort to have one prepared, I have not taken this class before)

The lab schedule and files will be available on my website, \url{https://www.jared-wallace.com}.
I will also post helpful links there. The calendar on the site will have holidays and
other academic events noted (like final day to drop, etc)

\section*{Grading}
Your lab grade will come primarily from the lab reports you submit. Specific breakdowns
will be enumerated in the lab handout.

The lab component is only part of your 3468 grade. Be sure to
check Dr. Gu's course syllabus for overall course grading criteria. If
you have an issue with a grade, or wish to see your grades for the semester so far,
please see me during office hours. If you have PGP setup on your mail client,
I can also email them to you. \textbf{I will not discuss grades during class}.

\section*{Drop Policy}
Be sure to refer to Dr. Gu's specific drop policy if you have any
questions. Understand that I only report your lab performance to Dr. Gu;
the grade you receive for this course will be assigned by Dr. Gu.
I recommend that you discuss your options individually with Dr. Gu
before dropping this course. Should you decide to drop, make sure you
drop both the lecture and lab components.

\section*{Attendance}
I don't think you want to miss any of these labs. I will drop the lowest
grade and replace it with the highest grade if you miss one or less labs.

\section*{Academic Integrity}
Each student is expected to do his/her own work on individual assignments
(these include all quizzes and the lab final exam). All students will be expected to
follow the University's Academic Integrity Policy. Any requirement that Dr. Gu
expects of his/her students with regards to academic honesty and
integrity will also be in place in the lab class. Please be sure to familiarize yourself
with this policy, and do not hesitate to ask Dr. Gu or myself if you
have any questions.

\section*{Students with Disabilities}
I will make every effort to comply with university's policy regarding making
accommodations for students with learning disabilities. If you are a student with a
disability who will require an accommodation(s) to participate in this course, please
contact me within the first two weeks of the semester. You will be asked to provide
documentation from the Office of Disability Services. Failure to contact me in a
timely manner may delay your accommodations.

\section*{Contact Information}
\begin{itemize}
    \item Lab Instructor: Jared Wallace
    \item Office: Comal 210B
    \item Office Hours: Monday, Wednesday and Friday from 8am-9am or by appointment
    \item E-mail: wallace@jared-wallace.com
    \item Webpage: jared-wallace.com
\end{itemize}
\end{document}
