\documentclass[letterpaper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}
\usepackage{courier}
\usepackage[margin=0.75in]{geometry}
\usepackage{listings}
\usepackage{color}
\usepackage{graphicx}
\usepackage[width=5in]{caption}
\usepackage{hyphenat}
\usepackage{hyperref}

% Format a sectionless paragraph
\newcommand*\unparagraph{
	\par
	\nopagebreak
	\vskip3.25ex plus1ex minus.2ex
	\noindent
}

% define extra colors
\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{purple}{RGB}{159,0,197}

% define the code listing format
\lstset{
	language=C++,
	basicstyle=\footnotesize\ttfamily,
	backgroundcolor=\color{white},
	showspaces=false,
	showstringspaces=false,
	frame=none,
	tabsize=3,
	keywordstyle=\color{purple},
	commentstyle=\color{dkgreen},
	stringstyle=\color{blue},
	escapeinside={\%*}{*)}
}

% efine the title/header
\title{\Large CS 1428\\Syllabus} 
\author{Jared Wallace}
\date{}

\begin{document}

\maketitle

\vspace{30mm}

\section*{Meeting time and place}
Wednesday at 4:30pm in Derrick Hall 236

\section*{Course Information}
A hands on opportunity to practice coding by completing lab activities.
We will be doing some very interesting labs this semester.
\section*{Recommendations}
I highly recommend you attend every class. Several labs build upon previously completed
labs. The lab schedule and files will be available on my website, \url{https://www.jared-wallace.com}.
I will also post helpful links there. The calendar on the site will have holidays and
other academic events noted (like final day to drop, etc).

You are highly encouraged to work together in class, although each person must
submit their work separately.

\section*{Grading}
Your lab grade will come primarily from the programs you submit. Specific breakdowns
will be enumerated in the lab handout.

For your lab grade, 20 percent will come from quizzes, 50 percent from the labs,
25 percent from your final, and five percent from attendance.

The lab component is only part of your 1428 grade. Be sure to
check Dr. Qasem's course syllabus for overall course grading criteria. If
you have an issue with a grade, or wish to see your grades for the semester so far,
please see me during office hours. If you have PGP setup on your mail client,
I can also email them to you. \textbf{I will not discuss grades during class}.

\section*{Drop Policy}
Be sure to refer to Dr. Qasem's specific drop policy if you have any
questions. Understand that I only report your lab performance to Dr. Qasem;
the grade you receive for this course will be assigned by Dr. Qasem.
I recommend that you discuss your options individually with Dr. Qasem
before dropping this course. Should you decide to drop, make sure you
drop both the lecture and lab components.

\section*{Attendance}
I don't think you want to miss any of these labs. I will drop the lowest
grade, however.

\section*{Academic Integrity}
Each student is expected to do his/her own work on individual assignments
(these include all quizzes and the lab final exam). All students will be expected to
follow the University's Academic Integrity Policy. Any requirement that Dr. Qasem
expects of his/her students with regards to academic honesty and
integrity will also be in place in the lab class. Please be sure to familiarize yourself
with this policy, and do not hesitate to ask Dr. Qasem or myself if you
have any questions.

\section*{Students with Disabilities}
I will make every effort to comply with university's policy regarding making
accommodations for students with learning disabilities. If you are a student with a
disability who will require an accommodation(s) to participate in this course, please
contact me within the first two weeks of the semester. You will be asked to provide
documentation from the Office of Disability Services. Failure to contact me in a
timely manner may delay your accommodations.

\section*{Contact Information}
\begin{itemize}
    \item Lab Instructor: Jared Wallace
    \item Office: Comal 210B
    \item Office Hours: Monday, Wednesday and Friday from 8am-9am or by appointment
    \item E-mail: wallace@jared-wallace.com
    \item Webpage: https://www.jared-wallace.com
\end{itemize}
\end{document}
